Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis

### 2020-08-25 Paperfolder/MDPI_submission/Revision01/Response/Response to the reviewers/Response to the reviewers.Rmd

---
title: Response to the reviewers
subtitle: Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis
author:  Chaochen Wang, Hiroshi Yatsuya, Yingsong Lin, Tae Sasakabe, Sayo Kawai, Shogo Kikuchi, Hiroyasu Iso, Akiko Tamakoshi
# date:  " updated `r Sys.Date()`"
output:
  redoc::redoc:
    highlight_outputs: TRUE
    margins: 1 
    line_numbers: FALSE 
---

@@

*The manuscript by C Wang et al includes a cohort of 94385 men and women from Japan, free from self-reported history of stroke, cancer, myocardial infarction and other types of heart disease at baseline who answered an FFQ regarding milk consumption. Between baseline in 1988-90 and end of follow-up in 2009, 2675 deaths from stroke were recorded on death registers. The authors applied Bayesian survival analysis to calculate hazard ratios and acceleration factors. With a range of milk consumption from “never” to “almost daily”, a higher milk consumption was associated with lower hazard and speed from dying from total stroke among men but not among women.*

*I have the following comments and questions for the authors:*

- *The introduction and discussion should however be more clear about the fact that the study is being performed in the lower range of the milk intake distribution. The dose-response meta-analysis in reference 2 indicates that the association may be non-linear. It would be good if the authors in more detail compared their results with other studies using fatal stroke as outcome and perhaps also focus on those cohorts with a low milk intake. For example, please elaborate on references 6, 20-23 in the discussion. Some of the references do not investigate milk intake per se. In the discussion, please specify that reference 19 does not investigate stroke mortality but CVD and all-cause mortality.*

[Response:] Thanks for pointing these out. We have updated the introduction as well as the discussion parts in order to better showing that these participants actually represent those in the lower range of milk intake. Discussion comparing our findings with previous studies conducted in East Asian population has been expanded in more details. The fact that reference 19 (currently reference 16) was looking into CVD and all-cause mortality has been clarified.

@@

- *Please specify age at baseline in abstract and methods.*

[Response:] Age range are now added in the abstract and methods accordingly.

- *Outcome ascertainment: Information on cause of death was from death certificates. Is there a possibility of individual linkage of the FFQ responses to a cause of death registry or were each of the participants’ death certificates reviewed? How many died from other causes, how many moved from the study area (and were thus lost to follow-up) and how many were censored at the end of follow-up (alive). Has stroke mortality changed during follow-up? Is there a difference in time trends of stroke subtype mortality? In how many cases was stroke subtype not recorded? The authors should also discuss potential reasons for differences in the results for stroke subtypes.*

[Response:] We have added these detailed information at the beginning of the results section. In the study area, investigators conducted systematic review of death certificates till the end of 2009. Date and cause of death were confirmed with the permission of the Director-General of the Prime Minister's Office. Number of deaths from causes other than stroke were 18868 (10731 men and 8137 women); 5493 (2022 men and 3471 women) dropped out from the follow-up (5.8%); 67349 (25281 men and 42068 women) were censored at the end of follow-up (71.4%). Among the 2675 stroke mortality confirmed in the JACC study, 766 were unfortunately not recorded with subtypes. The median (IQR) of follow-up years for cerebral infarction mortality were 11.2 (7.1, 15.3) and 11.8 (7.9, 16.4) in men and women; the median (IQR) of follow-up years for hemorrhagic stroke mortality were 9.9 (5.4, 12.3) and 10.9 (5.9, 15.1) in men and women. Potential reasons for differences in the results for stroke subtypes are described in discussion.

- *I agree with the authors that presenting the results in the FFQ categories is a good option, rather than to calculate the amount of consumption. However, I wonder if there is some indication from the validation study as to how much is on average consumed in the higher categories of intake?*

[Response:] Thanks for your positive comments. The validation study of the FFQ used in the JACC study found that the median intake for a daily milk consumer was about 146 grams per day. This has been added in the first paragraph of "2.2 Exposure and the outcome of interest" section.

- *Why did you adjust for sleep duration, is that a factor that influences both milk intake and stroke mortality risk?*

[Response:] Thanks for pointing this out. Previous report (cited as below) using the same data showed that healthy lifestyle behaviors (including milk intake daily and proper sleep duration) were associated with CVD mortality and therefore, we also included sleep duration as one of the potential confounders.

Eri Eguchi, Hiroyasu Iso, Naohito Tanabe, Yasuhiko Wada, Hiroshi Yatsuya, Shogo Kikuchi, Yutaka Inaba, Akiko Tamakoshi, on behalf of the Japan Collaborative Cohort Study Group, Healthy lifestyle behaviours and cardiovascular mortality among Japanese men and women: the Japan collaborative cohort study, European Heart Journal, Volume 33, Issue 4, February 2012, Pages 467–477.

- *The manuscript has minor language errors throughout and would benefit from a language review.*

[Response:] Many thanks for your detailed comments that helped us in improving the quality and readability of our manuscript. We tried our best to check and fixed the language errors throughout the revised version of the paper.

### 2020-08-25 ForReport20200114/HandOutEng.Rmd
updated handouteng
updated responses, files for latexdiff, manuscripts

@@

MData <- MILK_0 %>%
  filter(APO_hist != "TRUE" & IscheHeart != "TRUE" & 
           OtheHeart != "TRUE" & Can_hist != "TRUE" & MI_hist != "TRUE" & !is.na(Mlkfre)) %>% 
  select(Area, Age, Agegrp, tr_sex, ICD10, T_DX, Tot_Stroke, HemoStroke, IscheStroke, CHD, HeartF, MlkLogi, 
         Mlkfre, followpy, Smoking, Alc_Fre, BMI, BMIgrp, DM_hist, HT_hist, KID_hist, 
         LIV_hist, Exercise, Engy, ENERGY, Sleep, Slepgrp, Spi, Fru, Gretea, Cofe, Educ,
         Educgrp, Menopause)

@@

- N of total stroke mortality (I60-I69) confirmed: 2675 (1352 men and 1323 women)
\newpage
- Subtypes of stroke and CHD, heart failure: 
    - Ischemic stroke: 957 (520 men and 437 women);
    - Hemorrhagic stroke: 952 (432 men and 520 women);
    - CHD: 1320 (749 men and 571 women);
    - Heart failure: 1097 (498 men and 599 women).

@@

```{r datapre8, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE}
MData %>% 
  group_by(tr_sex, Tot_Stroke) %>% 
  summarise(n= n(), MeanFolYear = mean(followpy), MedianFolYear = median(followpy), MaxFolYear = max(followpy))
```

>>>>

  mutate(Death = if_else(T_DX > 1, "dropped", "deaths")) %>% 

@@

MData <- MILK_0 %>%
  filter(APO_hist != "TRUE" & IscheHeart != "TRUE" & 
           OtheHeart != "TRUE" & Can_hist != "TRUE" & MI_hist != "TRUE" & !is.na(Mlkfre)) %>% 
  select(Area, Age, Agegrp, tr_sex, ICD10, T_DX, Tot_Stroke, HemoStroke, IscheStroke, CHD, HeartF, MlkLogi, Death, 
         Mlkfre, followpy, Smoking, Alc_Fre, BMI, BMIgrp, DM_hist, HT_hist, KID_hist, 
         LIV_hist, Exercise, Engy, ENERGY, Sleep, Slepgrp, Spi, Fru, Gretea, Cofe, Educ,
         Educgrp, Menopause)

@@

- N of total stroke mortality (I60-I69) confirmed: 2675 (1352 men and 1323 women)
\newpage
- Numbers of individuals dropped out from follow-up
- Subtypes of stroke and CHD, heart failure: 
    - Ischemic stroke: 957 (520 men and 437 women);
    - Hemorrhagic stroke: 952 (432 men and 520 women);
    - CHD: 1320 (749 men and 571 women);
    - Heart failure: 1097 (498 men and 599 women).

@@

```{r datapre8, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, eval=TRUE}
MData %>% 
  group_by(tr_sex, Tot_Stroke) %>% 
  summarise(n= n(), MeanFolYear = mean(followpy), MedianFolYear = median(followpy), minFolYear = min(followpy), MaxFolYear = max(followpy))

MData %>% 
  group_by(tr_sex, IscheStroke) %>% 
  summarise(n= n(), MeanFolYear = mean(followpy), MedianFolYear = median(followpy), minFolYear = min(followpy), MaxFolYear = max(followpy), qs = quantile(followpy, c(0.25, 0.75)), prob = c(0.25, 0.75))

MData %>% 
  group_by(tr_sex, HemoStroke) %>% 
  summarise(n= n(), MeanFolYear = mean(followpy), MedianFolYear = median(followpy), minFolYear = min(followpy), MaxFolYear = max(followpy), qs = quantile(followpy, c(0.25, 0.75)), prob = c(0.25, 0.75))

### 2020-08-25 Paperfolder/Paperfolder.Rmd
updated responses, files for latexdiff, manuscripts

The causes and date of death were obtained from death certificates and were systematically reviewed. The follow-up period was defined as from the time of the baseline survey was completed, which was between 1988-1990, until the end of 2009 (administrative censor), or the date when move-out of study area, or the date of death from stroke recorded, whichever occurred first. Other causes of death were treated as censored and assumed not informative. The causes of death were coded by the 10th Revision of the International Statistical Classification of Diseases and Related Health Problems (ICD-10), therefore stroke was defined as I60-I69. We further classified these deaths into hemorrhagic stroke (I60, I61 and I62) or cerebral infarction (I63) when subtypes of stroke in their death certificates were available.

@@

The total follow-up was 1555073 person-years (median = 19.3 years), during which 2675 death from stroke was confirmed (1352 men and 1323 women). Among these stroke mortality, 952 were hemorrhagic stroke (432 men and 520 women), and 957 were cerebral infarction (520 men and 437 women). Age-adjusted stroke mortality rates for each category of milk intake frequency was estimated to be 1.8, 2.0, 1.7, 1.6, 1.5 per 1000 person-year for men and 1.3, 1.4, 1.2, 1.1, 1.2 per 1000 person-year for women.

@@

Detailed results from the Bayesian survival models (crude, age-adjusted and multivariable-adjusted) according to the frequency of milk intake separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and \textbf{Table \ref{tab:tab3}} (women). Compared to those who never had milk, both men and women had slower speed and lower hazard of dying from total stroke in crude models. Velocities that milk consumers dying from stroke is slower by a crude acceleration factor (AF) between 0.79 (sd = 0.05; 95% CrI: 0.74, 0.90) and 0.93 (sd = 0.04; 95% CrI: 0.85, 1.02) compared with non-consumers. Chances that the posterior crude HRs were estimated to be lower than 1 for those who had at least 1-2 times/month was higher than 86.5% in men and greater than 94.6% in women. However, lower hazard and delayed time-to-event was observed to remain after age or multivariable adjustment only among daily male milk consumers. Specifically, the mean (sd; 95% CrI) of posterior multivariable-adjusted AF and HR for daily male consumers of milk were 0.88 (sd = 0.05; 95% CrI: 0.81, 0.96) and 0.80 (sd = 0.07; 95% CrI: 0.69, 0.93) with a probability of 99.0% to be smaller than the null value (=1). Daily female milk consumers had posterior AFs and HRs that were distributed with means of 0.97 (sd = 0.09; 95% CrI: 0.88, 1.10) and 0.95 (sd = 0.12; 95% CrI: 0.80, 1.17) which had about 78.0% of chance that their HRs could be smaller than 1.

@@

>>>>

In the study area, investigators conducted systematic review of death certificates till the end of 2009. Date and cause of death were confirmed with the permission of the Director-General of the Prime Minister's Office. The follow-up period was defined as from the time of the baseline survey was completed, which was between 1988-1990, until the end of 2009 (administrative censor), or the date when move-out of study area, or the date of death from stroke recorded, whichever occurred first. Other causes of death were treated as censored and assumed not informative. The causes of death were coded by the 10th Revision of the International Statistical Classification of Diseases and Related Health Problems (ICD-10), therefore stroke was defined as I60-I69. We further classified these deaths into hemorrhagic stroke (I60, I61 and I62) or cerebral infarction (I63) when subtypes of stroke in their death certificates were available.

@@

The total follow-up was 1555073 person-years (median = 19.3 years), during which 2675 deaths from stroke were confirmed (1352 men and 1323 women). Among these stroke mortality, 952 were hemorrhagic stroke (432 men and 520 women), and 957 were cerebral infarction (520 men and 437 women). Number of deaths from causes other than stroke were 18868 (10731 men and 8137 women); 5493 (2022 men and 3471 women) dropped out from the follow-up (5.8%); 67349 (25281 men and 42068 women) were censored at the end of follow-up (71.4%). The median (interquartile range, IQR) of follow-up years for hemorrhagic stroke mortality were 9.9 (5.4, 12.3) in men and 10.9 (5.9, 15.1) in women; the median (IQR) of follow-up years for cerebral infarction mortality were 11.2 (7.1, 15.3) and 11.8 (7.9, 16.4) in men and women. Age-adjusted stroke mortality rates for each category of milk intake frequency was estimated to be 1.8, 2.0, 1.7, 1.6, 1.5 per 1000 person-year for men and 1.3, 1.4, 1.2, 1.1, 1.2 per 1000 person-year for women.

@@

Detailed results from the Bayesian survival models (crude, age-adjusted and multivariable-adjusted) according to the frequency of milk intake separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and \textbf{Table \ref{tab:tab3}} (women). Compared to those who never had milk, both men and women had slower speed and lower hazard of dying from total stroke in crude models. Velocities that milk consumers dying from stroke is slower by a crude acceleration factor (AF) between 0.79 (sd = 0.05; 95% CrI: 0.74, 0.90) and 0.93 (sd = 0.04; 95% CrI: 0.85, 1.02) compared with non-consumers. Chances that the posterior crude HRs were estimated to be lower than 1 for those who had at least 1-2 times/month was higher than 86.5% in men and greater than 94.6% in women. However, lower hazard and delayed time-to-event was observed to remain after age or multivariable adjustment only among daily male

@@

\noindent
milk consumers. Specifically, the mean (sd; 95% CrI) of posterior multivariable-adjusted AF and HR for daily male consumers of milk were 0.88 (sd = 0.05; 95% CrI: 0.81, 0.96) and 0.80 (sd = 0.07; 95% CrI: 0.69, 0.93) with a probability of 99.0% to be smaller than the null value (=1). Daily female milk consumers had posterior AFs and HRs that were distributed with means of 0.97 (sd = 0.09; 95% CrI: 0.88, 1.10) and 0.95 (sd = 0.12; 95% CrI: 0.80, 1.17) which had about 78.0% of chance that their HRs could be smaller than 1.
